Normalization by Evaluation for Call-By-Push-Value and Polarized Lambda Calculus

### 2019-05-10 ppdp19/ppdp19.tex
[ ppdp19 ] DBLP entries for new citations

Filinski \cite{filinski:tlca01} studied NbE for Moggi's computational lambda
calculus \cite{moggi:infcomp91}, shedding light on the difference
between call-by-name (CBN) and call-by-value (CBV) NbE, where Danvy's
type-directed partial evaluation \cite{danvy:popl96} falls into the
latter class.  The contribution of the computational lambda calculus
is to make explicit where the monad is invoked during monadic
evaluation, and this placement of the monad carries over to the NbE
setting.  Moggi's studies were continued by Levy \cite{levy:hosc06}
who designed the call-by-push-value (CBPV) lambda-calculus to embed
both the CBN and CBV lambda calculus.  Equational theories and
reduction-based normalization for CBPV were recently studied and
formalized in Coq~\cite{rizkallah2018formal,forster2019call}.
% TODO: improve last sentence.

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{auto-ppdp19}

>>>>

Filinski \cite{filinski:tlca01} studied NbE for Moggi's computational lambda
calculus \cite{moggi:infcomp91}, shedding light on the difference
between call-by-name (CBN) and call-by-value (CBV) NbE, where Danvy's
type-directed partial evaluation \cite{danvy:popl96} falls into the
latter class.  The contribution of the computational lambda calculus
is to make explicit where the monad is invoked during monadic
evaluation, and this placement of the monad carries over to the NbE
setting.  Moggi's studies were continued by Levy \cite{levy:hosc06}
who designed the call-by-push-value (CBPV) lambda-calculus to embed
both the CBN and CBV lambda calculus.  Equational theories and
reduction-based normalization for CBPV were recently studied and
formalized in Coq~\cite{rizkallahGarbuzovZdancewic:itp18,forsterSchaeferSpiesStark:cpp19}
% TODO: improve last sentence.

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{auto-ppdp19,byhand}
